This is an example of article title

### 2019-06-02 paper/paper.tex
jl2
jll

Sorting is a fundamental programming problem with many important applications. While there are well-known sorting algorithms for conventional computers, special techniques are required to take the most out of real hardware offering features such as cache memory and instruction-level parallelism. ChipSort is a Julia module for SIMD and cache-aware sorting. It implements sorting networks and bitonic merge networks with SIMD instructions, with configurable vector sizes. It also implements Combsort, which lends itself easily to vectorization and can achieve good performance depending on the memory access cost. Insertion sort is used to finalize. Large arrays are approached with a multi-way Mergesort. The implementation of ChipSort itself is of interest from a programming languages perspective due to its use of metaprogramming, more specifically Julia's generated functions. This enables custom code generation for different tasks and hardware at run-time, a feat owed to Julia. This article presents the implemented techniques as well as experiments that demonstrate speed gains compared to multiple standard libraries.

@@

This article presents \chipsort, a Julia module that implements SIMD and cache-aware sorting utilizing some of the techniques found in the literature. These include sorting and merging networks, the use of Combsort for medium sized arrays and of multi-way merging for large arrays. These techniques require not only tuning parameters such as vector and array sizes, but also generating specific code when implementing different size networks. \chipsort seeks to generate efficient custom code for each task, relying on Julia metaprogramming capabilities for that.

>>>>

Sorting is a fundamental programming problem with many important applications. While there are well-known sorting algorithms for conventional computers, special techniques are required to take the most out of real hardware offering features such as cache memory and instruction-level parallelism. ChipSort.jl is a Julia module for SIMD and cache-aware sorting. It implements sorting networks and bitonic merge networks with SIMD instructions, with configurable vector sizes. It also implements Combsort, which lends itself easily to vectorization and can achieve good performance depending on the memory access cost. Insertion sort is used to finalize. Large arrays are approached with a multi-way Mergesort. The implementation of ChipSort itself is of interest from a programming languages perspective due to its use of metaprogramming, more specifically Julia's generated functions. This enables custom code generation for different tasks and hardware at run-time, a feat owed to Julia. This article presents the implemented techniques as well as experiments that demonstrate speed gains compared to multiple standard libraries.

@@

This article presents {\tt ChipSort.jl}, a Julia module that implements SIMD and cache-aware sorting utilizing some of the techniques found in the literature. These include sorting and merging networks, the use of Combsort for medium sized arrays and of multi-way merging for large arrays. These techniques require not only tuning parameters such as vector and array sizes, but also generating specific code when implementing different size networks. \chipsort seeks to generate efficient custom code for each task, relying on Julia metaprogramming capabilities for that.
